QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-3.tex
ambros is right: it's not sure that the largest possible set has been reached
- further, there is no clear definition what *the* main intl. mailing lists are

In this section we describe the procedure we adopted to gather the
instances. In January $2014$, we issued an online call for instances
using the main international mailing lists of the mathematical
optimization and numerical analysis communities, reaching in this way
the largest\todo{AG: a large?} possible set of interested researchers and practitioners.
The call remained open for ten months, during which we received a large
number of contributions of different nature. The instances we gathered
come both from theoretical studies as well as from real-world
applications.

>>>>

In this section we describe the procedure we adopted to gather the
instances. In January $2014$, we issued an online call for instances
using main international mailing lists of the mathematical
optimization and numerical analysis communities, reaching in this way
a \textcolor{red}{large set of possibly interested} researchers and practitioners.
The call remained open for ten months, during which we received a large
number of contributions of different nature. The instances we gathered
come both from theoretical studies as well as from real-world
applications.
